# Missing values

```{r, include=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # set to local directory
source("srcs/helpers.R")
load(file = "data/processing/imdb_sample.RData")
load(file = "data/processing/imdb.RData")
```


## Missing value recognition

First we need to understand how the NA is encoded in the dataset. So we calculate 15 most common value among each columns:

```{r}
imdb_sample %>%
  mutate_all(~as.character(.)) %>%
  pivot_longer(1:ncol(.)) %>%
  group_by(name, value) %>%
  summarise(nunique = n()) %>%
  group_by(name) %>%
  arrange(-nunique) %>%
  slice(1:15) %>%
  get_DT(default_show = 5)
```

- Apparently, `\N`, for example, is likely to be one kind of tag for missing value among:

```r
SIGN_of_MISSING <- c('\\N', "", "[]", "	#N/A", "#N/A")
```

```{r}
SIGN_of_MISSING <- c('\\N', "", "[]", "	#N/A", "#N/A")
imdb %>%
  mutate_all( ~ifelse(. %in% SIGN_of_MISSING, NA, .) ) %>%
  mutate_at("isAdult", ~ifelse(. %in% c('0', '1'), ., NA) ) -> imdb
```



## Missing glance

We first take a glance of the missingness.

- By columns: 

  ```{r}
  colSums(is.na(imdb)) %>%
    sort(decreasing = TRUE)
  ```

  - 7 columns are complete.
  
  - `endYear` and `runtimeMinutes` seem to be a severely missing columns.

  ```{r}
  imdb %>% 
    mutate(startYear = as.numeric(startYear)) %>%
    arrange(-startYear) %>%
    group_by(primaryTitle) %>%
    slice(1) %>% ungroup %>%
    arrange(-numVotes) %>%
    slice(1:50) %>%
    column_to_rownames("primaryTitle") -> imdb_mostvotes
  ```
  
  ```{r}
  rowSums(is.na(imdb_mostvotes)) %>%
    sort(decreasing = TRUE) 
  ```

- By rows & columns: we pick the 50 most popularly voted pieces of work, and check their missingness among all colomns:

  ```{r,fig.width=8,fig.height=8}
  tidyimdb <- imdb_mostvotes %>% 
      rownames_to_column("id") %>% 
      gather(key, value, -id) %>% 
      mutate(missing = ifelse(is.na(value), "yes", "no"))
  
  ggplot(tidyimdb, aes(x = key, y = fct_rev(id), fill = missing)) +
    geom_tile(color = "white") + 
    scale_fill_viridis_d(guide = guide_legend(reverse = TRUE)) + 
    theme_bw() +
    labs(y = "Movie",
         x = "Variable",
         fill = "NA or not",
         title = "Missing values by rows & columns") +
    theme_jace +
    theme(axis.text.x = element_text(angle = 20,
                                     hjust = 0.95,
                                     vjust = 0.9))
  ```

    1. Utmost 1 column is missing in these rows, which indicates that IMDB, who makes the data of popular videos available to public, has done a good job collecting them!

    2. NA in `endYear` is especially frequent. 
    
        - One possible explanation is that only TV series have `endYear` as an attribute. And we can see from the plot that Top voted videos are more likely to be movies than TV series.


## Missing plot

### Missing pattern summary

Then we draw the missing value plot we coded from the Problem Set 4.

```{r,fig.width=9,fig.height=7}
imdb %>%
  plot_missing(percent = T, long_axis = T)
```

The most prevalent missing pattern is indeed the missing endYear, accounting for about 70% of the cases, which is driven by the fact that the `endYear` variable is missing in nearly all of the samples. In addition, `runtimeMinutes` and `endYear` are frequently absent simultaneously, whereas `genres` and `startYear` are missing in minor amounts.


### Heatmap

<!-- ```{r} -->
<!-- x <- missing_data.frame(imdb_mostvotes) -->
<!-- image(x) -->
<!-- ``` -->

```{r}

imdb_mostvotes %>% 
  rownames_to_column("id") %>% 
  select(id,startYear,endYear, runtimeMinutes, averageRating, numVotes) %>%
  gather(key, value, -id) %>% 
  
  mutate(missing = ifelse(is.na(value), "yes", "no")) %>%
  as_tibble %>%
  
  group_by(key) %>% 
  mutate(value = as.numeric(value),
         non_missing_value = sum(ifelse(missing == "no", 1, 0)),
         Std = case_when(
           non_missing_value == 1 & missing == "no" ~ 0,
           T ~ (value-mean(value, na.rm = TRUE))/sd(value, na.rm = TRUE))) %>% 
  
  ungroup() %>%
  mutate(missing2 = ifelse(missing == "yes", 1, 0)) %>%

ggplot(aes(x = fct_reorder(key, -missing2, sum), y = fct_reorder(id, -missing2, sum), fill = Std)) +
  geom_tile(color = "white") + 
  scale_fill_gradient2(low = "blue", mid = "white", high ="yellow", na.value = "black") + 
  labs(title = "Heatmap of 50 popular videos",
       subtitle = "black represents na",
       x = "5 Numerical variables",
       y = "Title") +
  theme_bw() +
  center_title 

```

- We generated a heatmap based on the 50 most-voted works. All of the missings are for endYear with *True Detective* as an exception because only TV series has an endYear. 
- Compared with other popular films, *True Detective* has fewer number of votes, but a relatively high `averageRating` and `runtimeMinutes`. Long running time matches the nature of TV series.

## Insight about why NA happens

### Missing by Years

We first take a look at the missing values of `runtime` and `genres` by each of their launching year.

> Since the number of new movies vary a lot by years, we take a look into the missing ratios rather than values.

```{r}
imdb %>%
  select(startYear, genres, runtimeMinutes) %>%
  group_by(startYear) %>%
  summarise(total_movie = n(),
            miss_genres = sum(ifelse(is.na(genres), 1, 0)) / total_movie,
            miss_runtime = sum(ifelse(is.na(runtimeMinutes), 1, 0)) / total_movie) %>%
  mutate(startYear = as.numeric(startYear)) %>%
  filter(startYear < 2022) -> imdb_na_by_startyear

imdb_na_by_startyear %>%
ggplot() +
  aes(x = as.numeric(startYear),
      y = total_movie) +
  labs(title = "By-year NA pattern of run time and genres",
       x = "",
       y = "Total Movies") +
  geom_area(fill = "#007a8788") +
  scale_y_continuous(breaks = pretty_breaks(4)) +
  scale_x_continuous(breaks = pretty_breaks(10), limits = c(1880,NA)) +
  theme_jace -> p1

imdb_na_by_startyear %>%
ggplot() +
  aes(x = as.numeric(startYear),
      y = miss_runtime) +
  labs(x = "",
       y = "NA of Run Time") +
  geom_area(fill = "#6166B388") +
  scale_y_continuous(breaks = pretty_breaks(4), label = percent_format()) +
  scale_x_continuous(breaks = pretty_breaks(10), limits = c(1880,NA)) +
  theme_jace -> p2

imdb_na_by_startyear %>%
ggplot() +
  aes(x = as.numeric(startYear),
      y = miss_genres) +
  geom_area(fill = "#6166B388") +
  labs(x = "Launching Year",
       y = "NA of genres") +
  scale_y_continuous(breaks = pretty_breaks(4), label = percent_format()) +
  scale_x_continuous(breaks = pretty_breaks(10), limits = c(1880,NA)) +
  theme_jace  -> p3

p1 / p2 / p3
```

- From the first figure, we can see that the number of works is increasing by years (except for 2020 because of COVID-19). From the following 2 graphs, we can see that the amount of missing data for `runtimeMinutes` and `genres` are quite volatile. 

    - For `runtimeMinutes`, the missing percentage was high before 1960 may be due to technology reasons (but the sample size is small), and there is an increasing trend after 1960. 
  
    - For `genres`, it begins to decrease after the year of 2000. We can infer that the film market became more standardized and the industry has been benefited by the growth of technology.

### Missing by Genres

Let take a deeper look at the missing values of runtime by each of their genre to see if there are some patterns here:
  
```{r}
imdb %>%
  
  select(genres, runtimeMinutes) %>%
  mutate(miss_min = ifelse(is.na(runtimeMinutes), 1, 0)) %>%
  as.data.table() %>%
  separate_rows(genres) %>%
  group_by(genres) %>%
  summarise(total_movie = n(),
            miss_runtime = sum(miss_min))  -> imdb_na_by_genres

imdb_na_by_genres %>%
  mutate(miss_runtime = miss_runtime / total_movie) %>%
  mutate(genres=fct_reorder(genres, miss_runtime)) %>%
  
ggplot() +
   aes(x = genres,
       y = miss_runtime) +
  geom_col(fill = "#6166B388") +
  theme_jace +
  scale_y_continuous(labels = percent_format(1), 
                     breaks = breaks_width(0.1)) +
  only_x +
  coord_flip() +
  labs(x = "Genre",
       y = "NA of running time",
       title = "By-genre NA pattern of run time")
```

- We can see a significant difference between `genres`: 

    - Genres which are not usaully limited by run time, such as talk show and news, have the most missing runtimes as expected. 
    
    - On the contrary, films and noir nearly have no missing value in runtime, which are also as what we might be expecting.
